---
title: "Four Parameters: Categorical"
author: "Aashna"
format: html
execute:
  echo: false
---

```{r}
#| label: setup 
#| echo: FALSE 
#| message: FALSE
library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
```


```{r}
#| label: plot
tibble(sex = c("Female", "Male"))
ndata

fit_nes |> 
add_epred_draws(newdata = ndata) |> 
select(sex, .category, .epred) |>
ggplot(aes(x = .epred, fill = sex)) + 
geom_histogram(bins = 100) + 
facet_grid(~ .category) + 
scale_x_continuous(breaks = c(0.05, 0.3, 0.6), 
labels = scales::percent_format()) + 
labs(title = "Posterioir for Expected Probability of candidate Support Among Women", 
subtitle = "Women are most likely to support Clinton", 
x = "Posterior Probability of Expected Vote Probability", 
y = "Count")

```


```{r}
#| label: cleaning
#| echo: FALSE 
#| message: FALSE
nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot",
  ))
```

I've started analyzing voting behavior in the 1992 US Presidential election using the primer.data and tidyverse packages in R Markdown. By categorizing votes for Clinton, Bush, and Perot by sex, I'm investigating how these factors relate to voting patterns. A potential challenge is ensuring the dataset represents a diverse range of voters accurately, as underrepresentation could affect the validity of the analysis.

```{r}
#| label: model
#| cache: true

fit_nes <- \begin{aligned}
\rho_{clinton} &=& \frac{e^{\beta_{0, clinton} + \beta_{1, clinton} male}}{1 + e^{\beta_{0, clinton} + \beta_{1, clinton} male}}\\
\rho_{perot} &=& \frac{e^{\beta_{0, perot} + \beta_{1, perot} male}}{1 + e^{\beta_{0, perot} + \beta_{1, perot} male}}\\
\rho_{bush}  &=& 1 - \rho_{clinton} - \rho_{perot}
\end{aligned}

```

```{r}
#| label: table
tbl_regression(fit_nes)
```


I'm analyzing voting behavior in the 1992 US Presidential election using primer.data and tidyverse in R Markdown. By categorizing votes for Clinton, Bush, and Perot by sex, I'm investigating how these factors shape voting patterns. It's crucial to ensure the dataset accurately reflects diverse voter demographics to ensure the reliability of our conclusions. One key interest is determining the posterior probability of female voters supporting Clinton, providing a measure of uncertainty through Bayesian credible intervals. This helps us understand how gender influences candidate preference in this historical election context.





